\Title

### 2020-02-17 manuscript/manuscript.tex
Improve some text

\noindent where $\left\lVert \cdot \right\rVert ^ 2$ symbolizes the L$_2$ norm
and $\lambda_d$ is a \emph{damping} parameter that has the same dimension as
the Jacobian matrix elements.

@@

Misfit function from equation~\ref{eq:misfit} is solved through least squares.
If the number of observation points is equal or larger to the number of
sources, then the linear problem defined on equation~\ref{eq:linear-problem} is
well- or over-determined, respectively. Therefore, the scaled coefficients that
minimize the misfit function can be obtained through \citep{menke1989}:

@@

Once the scaled coefficients are obtained, the sources coefficients
$\mathbf{c}_\text{est}$ can be obtained by rescaling
$\hat{\mathbf{c}}_\text{est}$:

>>>>

\noindent where $\left\lVert \cdot \right\rVert ^ 2$ symbolizes the L$_2$ norm
and $\lambda_d$ is a \emph{damping} parameter with the same units as the
Jacobian matrix elements.

@@

Misfit function from equation~\ref{eq:misfit} is minimized through Cholesky
decomposition.
If the number of observation points is equal or larger to the number of
sources, then the linear problem defined on equation~\ref{eq:linear-problem} is
well- or over-determined, respectively. Therefore, the scaled coefficients that
minimize the misfit function can be obtained through \citep{menke1989}:

@@

Once the scaled coefficients are obtained, the sources' coefficients
$\mathbf{c}_\text{est}$ can be obtained by rescaling
$\hat{\mathbf{c}}_\text{est}$:
